
\pdfbookmark{Acknowledgements}{Acknowledgements}


\titlespacing*{name=\chapter,numberless}{0pt}{12mm}{12mm}
\chapter*{Acknowledgements}
\noindent

\newlength{\ackskip}
\setlength{\ackskip}{8pt}


\noindent
This thesis has only been possible through the support of a great many people, to whom I am indebted for their help, encouragement, guidance and company over the years. I am sincerely thankful, and I hope I can give back in equal measure at some point in time. Including you in this (necessarily incomplete) hat-tip is nowhere near enough, but you have to start somewhere.

\vspace{\ackskip}
\noindent
First and foremost, I want to thank my supervisor, Misha Ivanov, for his unwavering support and for sharing his unbridled enthusiasm for science and a treasure trove of crystal-clear insights. You have helped me grow as a scientist and as a person in ways~I only vaguely anticipated; thank you for this journey, and I look forward to the rest of the~road.

\vspace{\ackskip}
\noindent
I want to thank my parents for their steadfast support and their constant encouragement, as well as my brother for his amazing example of what one can and should do in life. I'm also deeply grateful to the various people that shared living in Europe with me over the years -- Andrea Alatorre, Diego Trujillo, Silvia and Ja\'s Elsner and your amazing children, Marlene Bruce, Georgina Galván, and David and Darío Alatorre~-- for providing a small bit of home away from home. Similarly, I want to thank María de la Luz García and Irene Pisanty for their warm support while home and at a distance.


\vspace{\ackskip}
\noindent
To the people at Imperial College who made my PhD a fun experience in a vibrant scientific environment, thank you for everything. I have a huge debt of gratitude with Bridgette Cooper, Jon Leeuwenburgh and Peter Hawkins for their close support since the beginning, and I want to thank David Butcher, Tom Siegel, Amelle Za\"ir, Emma Simpson, Martin Arnold, David Walke, Ksenia Katsanovskaja, Laila Bahmanpour, Luke Chipperfield, Dane Austin, Thomas Barillot, David Wood, Allan Johnson, Paloma Matía, Steffen Driever, Felicity McGrath, Vitali Averbukh, Jon Marangos, and many others for making the Laser Consortium a cool and interesting place to work. Thanks are also due to Miranda Smith, Judith Baylis and Marcia Salviato for their amazing skills at making problems go away.

\vspace{\ackskip}
\noindent
I'm enormously lucky to have met and worked with the rest of the CQD Wundercohort~-- Mark, Kyle, Howard, Mihai, Howard, Mercedes, Naomi, Devin, Jake, André, Darren and Joe, thanks for a wealth of cool ideas and interactions, from the Whiteley suite to Texas and beyond. Thanks also go to the many people I met over the years at Imperial, particularly to Celia, Aida, Aizar, and Elisa, as well as to Pauline, Marie, Maria Chiara, Juan Luis and Nelle for helping steer me, somewhat, away from~work.


\vspace{\ackskip}
\noindent
I'm especially grateful to Lisa Torlina and Olga Smirnova for their many shared insights and their support over the years, in what Lisa calls `spirited discussions' and I call `providing much of the basis for my work'. Thanks also go to the many cool people at MBI, including Felipe Morales, Maria Richter, Valeria Serbinenko, Alex Harvey, Zdenek Ma\v{s}in, Wilhelm Becker, Álvaro Jiménez, David Ayuso and Rui Silva, as well as Nora Molkentin, Frank Hellmann and Stijn van Tongeren for their oft-offered hospitality.


\vspace{\ackskip}
\noindent
A la pandilla: Rebeca, Sirio, Diego, Arturo, Rodrigo, Rosa, Yunuén, Ana, Héctor, Mario, Andrea, Elena, Tania, Mariel, Francisco, Velvet, y demás asociados, gracias por diez años de amistad, y vamos por los siguientes diez. 


\vspace{\ackskip}
\noindent
I also want to thank everyone at the Lightyear Foundation for the many amazing experiences shared with them. I want to thank Fran for her enormous faith in me, and Myf, Anisha, Saviour, Alex and Nesh for letting me be part of an amazing team starting something really special, as well as Erica, Chiara, Gavin, Louise, Yalda, Antonia, Aaron and Craig for teaching me a great deal about how to communicate science. The same goes for Nic Harrigan and Simon~Foster.

\vspace{\ackskip}
\noindent
I'm grateful to my scientific collaborators at other institutions, including Daniel Hickstein, Oren Cohen, Ofer Kfir, Avner Fleischer, Ben Galloway, and the Kapteyn-Murnane group, for interesting discussions over the years, as well as to Suren Sukiasyan for his helpful simulations. 

\vspace{\ackskip}
\noindent
To my mentors over the years, Eduardo Nahmad, Alan Downie and Juan Carlos Aguilar, thank you for teaching me to wonder at the world, and the discipline to make that wonder come to fruition. 

\vspace{\ackskip}
\noindent
Finally, I want to thank CONACyT, Imperial College and DFG for the financial support that made my PhD possible.


\vspace{\ackskip}
\noindent
And, as a last call: I am grateful to the tram tracks near the Karl-Ziegler-Straße station, for helping me find the time to finish the research presented here, albeit in slightly more painful a manner than I might have liked.




\vspace{1.25cm}

\hfill Laughter is the best medicine,

\hfill unless you have a broken rib.



















